A Spiking Independent Accumulator Model for Winner-Take-All Computation

### 2017-01-31 doc/paper/paper.tex
Prefer time-constant.
Forgot important minus.

\subsubsection{Principle 1: Representation}
We define the representation of a scalar value $x(t)$ by an encoding and decoding with respect to some population of neurons.
The encoding of $x(t)$ into a spike train $a_i(t)$ for neuron $i$ is given by:
\begin{equation}
    a_i(t) = G_i\left[\alpha_i e_i x(t) + J_i^{\mathrm{bias}}\right] ,
\end{equation}
where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
\begin{equation}
    \hat x(t) = \sum_i d_i \left[(a_i * h)(t)\right] ,
\end{equation}
where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
For the transmission of a value from one population to another, the connection weights are given by:
\begin{equation}
    W_{ij} = \alpha_j e_j d_i \text{.}
\end{equation}

@@

Interestingly, for all clear decisions the correct winner was determined by the LCA network.
Thus, a plot of correct trials looks identical to Figure~\ref{fig:decisions}, with slightly different error bars.
While always reaching a clear decision, the decisions of the IA network are not always correct.
Overall, the IA performance tends to be worse than the LCA performance for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
%A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
%In the NEF the neuron gain and bias parameters are usually picked from random distributions.
%As such the layer 2 populations will become active at slightly different thresholds.
%By using identical layer 2 populations, i.e., identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/correct}
    \caption{
        Fraction of correct trials for the IA network.
        Each plot shows data for a different combination of input magnitude $u$ and integration time constant $\tau_1$.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line indicates the optimum.
    }\label{fig:correct}
\end{figure*}

>>>>

\subsubsection{Principle 1: Representation}
We define the representation of a scalar value $x(t)$ by an encoding and decoding with respect to some population of neurons.
The encoding of $x(t)$ into a spike train $a_i(t)$ for neuron $i$ is given by:
\begin{equation}
    a_i(t) = G_i\left[\alpha_i e_i x(t) + J_i^{\mathrm{bias}}\right] ,
\end{equation}
where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
\begin{equation}
    \hat x(t) = \sum_i d_i \left[(a_i * h)(t)\right] ,
\end{equation}
where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(-t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
For the transmission of a value from one population to another, the connection weights are given by:
\begin{equation}
    W_{ij} = \alpha_j e_j d_i \text{.}
\end{equation}

@@

Interestingly, for all clear decisions the correct winner was determined by the LCA network.
Thus, a plot of correct trials looks identical to Figure~\ref{fig:decisions}, with slightly different error bars.
While always reaching a clear decision, the decisions of the IA network are not always correct.
Overall, the IA performance tends to be worse than the LCA performance for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
%A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
%In the NEF the neuron gain and bias parameters are usually picked from random distributions.
%As such the layer 2 populations will become active at slightly different thresholds.
%By using identical layer 2 populations, i.e., identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
\begin{figure*}[t]
    \centering
    \includegraphics{figures/correct}
    \caption{
        Fraction of correct trials for the IA network.
        Each plot shows data for a different combination of input magnitude $u$ and integration time-constant $\tau_1$.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line indicates the optimum.
    }\label{fig:correct}
\end{figure*}
